---
title: "Skeleton_of_Outputs"
author: ""
date: "3/19/2020"
output: pdf_document
---

This is a document for a code skeleton for the outputs section of the project.

Loading in relevant data sources for this: 
```{r, message=FALSE, echo=TRUE, warning=FALSE}

setwd('~/Dropbox/COVID-BaltimoreCity/Output_20200322_v2')

require(socialmixr)
require(xlsx)
require(magrittr)
require(stringr)
require(reshape2)
require(dplyr)
require(ggplot2) 
require(tidyr)
require(xtable)

#cleaning function, we want to take in incident symptomatic cases in each of the original 14 age groups and time the simulation has been running for (days since introduction to state) for each of the 500 simulations
#we want the function to return a matrix for each R_0 scenario that includes incident symptomatic infections for each of the 7 (consolidated) age categories over 365 days for each of the 500 simulations. 
complete_R017<- read.csv("SEIR_results__n500__r017__75.csv")
complete_R021<- read.csv("SEIR_results__n500__r021__75.csv")
complete_R025<- read.csv("SEIR_results__n500__r025__75.csv")

complete_R017<- complete_R017[-182501,]
complete_R021<- complete_R021[-182501,]
complete_R025<- complete_R025[-182501,]

load_and_clean<- function(data, r0val){
  complete_incident_r0val<- data%>%
    select(time,incid_I1,incid_I2,incid_I3,incid_I4,incid_I5,
         incid_I6,incid_I7,incid_I8,incid_I9,
         incid_I10,incid_I11,incid_I12,incid_I13,incid_I14)
  
  combined_incident_r0val<- complete_incident_r0val%>%
        mutate(cat1=rowSums(.[2:5]))%>%
        mutate(cat2=rowSums(.[6:8]))%>%
        mutate(cat3=rowSums(.[9]))%>%
        mutate(cat4=rowSums(.[10:12]))%>%
        mutate(cat5=rowSums(.[13]))%>%
        mutate(cat6=rowSums(.[14]))%>%
        mutate(cat7=rowSums(.[15]))
  
  combined_incident_r0val<- combined_incident_r0val%>%
    select(time, cat1, cat2, cat3, cat4, cat5, cat6, cat7)
  
  return(combined_incident_r0val)
}
  
combined_incident_R017<- load_and_clean(complete_R017,R017)  
combined_incident_R021<- load_and_clean(complete_R021,R021)  
combined_incident_R025<- load_and_clean(complete_R025,R025)  


```




```{r, message=FALSE, warning=FALSE, echo=TRUE}

#working probabilities for severe cases, hospitalization, ICU, vent and death. 
#these are nested conditional probabilities, and they rely on the following  assumptions: 
#the percentage of severe cases in each categories is obtained from CDC table where we combined the 55-74 age groups and the 75-80 and 80+ age groups. 
#we assume now that 100% of severe cases get hospitalized (this could be adjusted)
# the remainder of the nested probabilities come from the CDC table, instead of using the denominator as all the cases in that age group, we shift the denoinator to be the preceding categoriy of sverity so prob ICU is the number of icu cases for that age group/ number of hospitalized cases for that age group. 
#moreover, instead of having just a point estimate from the CDC table as described we take this point estmate to be the mean of a beta distribution, where the second shape parameter is 1. The first shape parameter is then defined by (mean)/(1-mean) where the mean is the point estimate of the nested probability obtained from the CDC table. 



#HCW workers and homeless have the same nested prob scheme as the 45-540y.o group.
prob_severe<- c(0.0256,0.263,0.395,0.577,1.732,0.577,0.577)

prob_hospitalized<- rep(1,7)

prob_ICU<- c(0,0.253,0.582,0.686,0.908,0.582,0.582)

prob_dead_from_icu<-c(0,0.041,0.071,0.217,0.445,0.071,0.071)

prob_vent_icu<- c(0,0.035,0.059,0.214,0.912,0.059,0.059)

prob_dead_from_vent<- c(0,0.33,0.25,0.692,1.27,0.25,0.25)

prob_matrix<- cbind(prob_severe,prob_hospitalized,prob_ICU,prob_dead_from_icu,
                     prob_vent_icu,prob_dead_from_vent)



```


Now calculate the number in of severe, hospitalized, ICU and vented infections at each timepoint (day) in each group (age groups 1-12 and healthcare workers and homeless). 


```{r, message=FALSE, echo=TRUE, warning=FALSE}
#calculate number of incident cases that get classified as severe,  of those, 
#the number get hospitalized (currently 100%), of that then those that get classified as ICU and then of those that get put on a vent and of those the ones that die 11 days later (11 day lag for death prob)
#this is for each age group (+ HCW and homeless)
#note this categorization is NOT a disease progression, a person gets assigned based on the worst state they could possibly reach. 


incident_classifications<- function(data, complete_data, R0val){
  counts_array_R0val<- array(NA, dim=c(nrow(data),ncol(data),5))
  counts_array_R0val[,1,]<- data$time
  
for(i in 2:ncol(data)){
  
  for(j in 1:365){
    if(j<=4){
counts_array_R0val[which(complete_data$time==j),i,1]<- 
      data[complete_data$time==j,i,1]*prob_matrix[i-1,1]
}
  else{
    counts_array_R0val[which(complete_data$time==j),i,1]<- 
      data[complete_data$time==(j-4),i,1]*prob_matrix[i-1,1]
  }


  }  
 counts_array_R0val[,i,2]<- counts_array_R0val[,i,1]*prob_matrix[i-1,2] 
 
for(k in 1:365){
     if(k<=4){      
counts_array_R0val[which(complete_data$time==k),i,3]<- 
      counts_array_R0val[which(complete_data$time==k),i,2]*prob_matrix[i-1,3]
     }
  else{
   counts_array_R0val[which(complete_data$time==k),i,3]<- 
      counts_array_R0val[which(complete_data$time==(k-4)),i,2]*prob_matrix[i-1,3] 
  }
}
 
 for(l in 1:365){
        if(l<=3){
counts_array_R0val[which(complete_data$time==l),i,4]<- 
      counts_array_R0val[which(complete_data$time==(l)),i,3]*prob_matrix[i-1,5] 
        }
   else{
     counts_array_R0val[which(complete_data$time==l),i,4]<- 
      counts_array_R0val[which(complete_data$time==(l-3)),i,3]*prob_matrix[i-1,5] 
   }
 }
 
 for(m in 1:365){
   if(m<=5){
     counts_array_R0val[which(complete_data$time==m),i,5]<- 
      (counts_array_R0val[which(complete_data$time==(m)),i,3]*prob_matrix[i-1,4])+(counts_array_R0val[which(complete_data$time==(m)),i,4]*prob_matrix[i-1,6])
   }
   
 else if(m>5&m<=8){
   counts_array_R0val[which(complete_data$time==m),i,5]<- 
      (counts_array_R0val[which(complete_data$time==(m)),i,3]*prob_matrix[i-1,4])+(counts_array_R0val[which(complete_data$time==(m-5)),i,4]*prob_matrix[i-1,6])
 }
 else{
   counts_array_R0val[which(complete_data$time==m),i,5]<- 
      (counts_array_R0val[which(complete_data$time==(m-8)),i,3]*prob_matrix[i-1,4])+(counts_array_R0val[which(complete_data$time==(m-5)),i,4]*prob_matrix[i-1,6])
 }
 }
}


 
return(counts_array_R0val)

}

counts_array_R017<- incident_classifications(combined_incident_R017,complete_R017,R017)
counts_array_R021<- incident_classifications(combined_incident_R021,complete_R021,R021)
counts_array_R025<- incident_classifications(combined_incident_R025,complete_R025,R025)


```

Now  load in a dataset that gives estimates of how long people stay hospitalized, in ICU or on vents
Compute a running total of each category.
```{r,message=FALSE, warning=FALSE, echo=TRUE}
#for now we are supposing we get a point estimate to determine how long people stay in each of the states. 

length_of_stay<- c(NA,12,8,11,NA)

#now we want a running total of how many severe cases, hospitalizations, ICU, vents, and deaths are occuring we are keeping people in hospital, or ICU, or on a vent for 11 days (i.e. fixed point estimate, this can be adapted to be a distribution). We do this for each day in each of the 500 sims, we will compute summary statistics seperately. 
cumulative_counts<- function(data, R0val){
  cumulative_array_R0val<- array(NA, dim=dim(data))
  
  cumulative_array_R0val[,1,]<- data[,1,]

  for(j in 2:dim(cumulative_array_R0val)[2]){
    cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==1),j,]<-
      data[which(data[,1,1]==1),j,]
    
    for(i in 2:365){
      cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==i),j,1]<-
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(i-1)),j,1]+
        data[which(data[,1,1]==i),j,1]
      cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==i),j,5]<-
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(i-1)),j,5]+
        data[which(data[,1,1]==i),j,5]
    }

    for(k in 2:365){
      if(k<=length_of_stay[2]){
      cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==k),j,2]<-
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(k-1)),j,2]+
        data[which(data[,1,1]==k),j,2]
      }
      else {
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==k),j,2]<-
          cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==k-1),j,2]+
          data[which(data[,1,1]==k),j,2]-data[which(data[,1,1]==(k-length_of_stay[2])),j,2]
      }
    }
  for(l in 2:365){
      if(l <= length_of_stay[3]){
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==l),j,3]<-
          cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(l-1)),j,3]+
          data[which(data[,1,1]==l),j,3]
      }
    else{
      cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==l),j,3]<-
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(l-1)),j,3]+
          data[which(data[,1,1]==l),j,3]-data[which(data[,1,1]==(l-length_of_stay[3])),j,3]
    }
  }
    for(m in 2:365){
    if(m<=length_of_stay[4]){
      cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==m),j,4]<-
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(m-1)),j,4]+
        data[which(data[,1,1]==m),j,4]
    }
    else{
      cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==m),j,4]<-
        cumulative_array_R0val[which(cumulative_array_R0val[,1,1]==(m-1)),j,4]+
          data[which(data[,1,1]==m),j,4]-data[which(data[,1,1]==(m-length_of_stay[4])),j,4]
      }
    }
   
}
return(cumulative_array_R0val)
  
}

cumulative_array_R017<- cumulative_counts(counts_array_R017,R017)
cumulative_array_R021<- cumulative_counts(counts_array_R021,R021)
cumulative_array_R025<- cumulative_counts(counts_array_R025,R025)

```


```{r, message=FALSE, warning=FALSE, echo=TRUE}

#get median and 75th and 25th quantile for each output, incident and cumulative counts. 

#this is the part where we could get fancy and do a bootstrap median, min and max??? if we wanted. eventually....

median_incident_symptomatic<- function(data, R0val){
  median_incident_combined_R0val<- matrix(NA,365,ncol(data))

    for(i in 1:nrow(median_incident_combined_R0val)){
      median_incident_combined_R0val[i,]<-
        apply(data[which(data[,1]==i),],2,median)
    }
  upper_incident_combined_R0val<- matrix(NA,365,ncol(data))

    for(i in 1:nrow(upper_incident_combined_R0val)){
      upper_incident_combined_R0val[i,]<-
        apply(data[which(data[,1]==i),],2,quantile, probs=(0.75), na.rm=TRUE)
    }
  
  lower_incident_combined_R0val<- matrix(NA,365,ncol(data))

    for(i in 1:nrow(lower_incident_combined_R0val)){
      lower_incident_combined_R0val[i,]<-
        apply(data[which(data[,1]==i),],2,quantile, probs=(0.25), na.rm=TRUE)
    }
  
  
  return(list(median_incident_combined_R0val, upper_incident_combined_R0val,
              lower_incident_combined_R0val))
  }

incident_symptomatic_R017<- median_incident_symptomatic(combined_incident_R017,R017)

median_incident_symptomatic_R017<- incident_symptomatic_R017[[1]]
upper_incident_symptomatic_R017<- incident_symptomatic_R017[[2]]
lower_incident_symptomatic_R017<- incident_symptomatic_R017[[3]]


incident_symptomatic_R021<- median_incident_symptomatic(combined_incident_R021,R021)
median_incident_symptomatic_R021<- incident_symptomatic_R021[[1]]
upper_incident_symptomatic_R021<- incident_symptomatic_R021[[2]]
lower_incident_symptomatic_R021<- incident_symptomatic_R021[[3]]

incident_symptomatic_R025<- median_incident_symptomatic(combined_incident_R025,R025)
median_incident_symptomatic_R025<- incident_symptomatic_R025[[1]]
upper_incident_symptomatic_R025<- incident_symptomatic_R025[[2]]
lower_incident_symptomatic_R025<- incident_symptomatic_R025[[3]]

####################################################################

median_counts_array<- function(data, R0val){
  median_counts_array<- array(NA, dim=c(365,dim(data)[2], dim(data)[3]))
  
  for(i in 1:dim(median_counts_array)[3]){
    for(j in 1:dim(median_counts_array)[1]){
      median_counts_array[j,,i]<- apply(data[which(data[,1,1]==j),,i],2,median)
    }
  }
 
   upper_counts_array<- array(NA, dim=c(365,dim(data)[2], dim(data)[3]))
  
  for(i in 1:dim(upper_counts_array)[3]){
    for(j in 1:dim(upper_counts_array)[1]){
      upper_counts_array[j,,i]<- apply(data[which(data[,1,1]==j),,i],2,quantile, prob=0.75,na.rm=T)
    }
  } 
   
    lower_counts_array<- array(NA, dim=c(365,dim(data)[2], dim(data)[3]))
  
  for(i in 1:dim(lower_counts_array)[3]){
    for(j in 1:dim(lower_counts_array)[1]){
      lower_counts_array[j,,i]<- apply(data[which(data[,1,1]==j),,i],2,quantile, prob=0.25,na.rm=T)
    }
  } 
    return(list(median_counts_array, upper_counts_array,lower_counts_array))
}

summary_counts_array_R017<- median_counts_array(counts_array_R017,R017)
median_counts_array_R017<- summary_counts_array_R017[[1]]
upper_counts_array_R017<- summary_counts_array_R017[[2]]
lower_counts_array_R017<- summary_counts_array_R017[[3]]

summary_counts_array_R021<- median_counts_array(counts_array_R021,R021)
median_counts_array_R021<- summary_counts_array_R021[[1]]
upper_counts_array_R021<- summary_counts_array_R021[[2]]
lower_counts_array_R021<- summary_counts_array_R021[[3]]

summary_counts_array_R025<- median_counts_array(counts_array_R025,R025)
median_counts_array_R025<- summary_counts_array_R025[[1]]
upper_counts_array_R025<- summary_counts_array_R025[[2]]
lower_counts_array_R025<- summary_counts_array_R025[[3]]
########################################

median_cumulative_array<- function(data, R0val){
  median_cumulative_array<- array(NA, dim=c(365,dim(data)[2], dim(data)[3]))
  
  for(i in 1:dim(median_cumulative_array)[3]){
    for(j in 1:dim(median_cumulative_array)[1]){
      median_cumulative_array[j,,i]<- apply(data[which(data[,1,1]==j),,i],2,median,na.rm=T)
    }
  }
 
   upper_cumulative_array<- array(NA, dim=c(365,dim(data)[2], dim(data)[3]))
  
  for(i in 1:dim(upper_cumulative_array)[3]){
    for(j in 1:dim(upper_cumulative_array)[1]){
      upper_cumulative_array[j,,i]<- apply(data[which(data[,1,1]==j),,i],2,quantile, prob=0.75,na.rm=T)
    }
  } 
   
    lower_cumulative_array<- array(NA, dim=c(365,dim(data)[2], dim(data)[3]))
  
  for(i in 1:dim(lower_cumulative_array)[3]){
    for(j in 1:dim(lower_cumulative_array)[1]){
      lower_cumulative_array[j,,i]<- apply(data[which(data[,1,1]==j),,i],2,quantile, prob=0.25,na.rm=T)
    }
  } 
    return(list(median_cumulative_array, upper_cumulative_array,lower_cumulative_array))
}


summary_cumulative_array_R017<- median_cumulative_array(cumulative_array_R017,R017)
median_cumulative_array_R017<- summary_cumulative_array_R017[[1]]
upper_cumulative_array_R017<- summary_cumulative_array_R017[[2]]
lower_cumulative_array_R017<- summary_cumulative_array_R017[[3]]

summary_cumulative_array_R021<- median_cumulative_array(cumulative_array_R021,R021)
median_cumulative_array_R021<- summary_cumulative_array_R021[[1]]
upper_cumulative_array_R021<- summary_cumulative_array_R021[[2]]
lower_cumulative_array_R021<- summary_cumulative_array_R021[[3]]

summary_cumulative_array_R025<- median_cumulative_array(cumulative_array_R025,R025)
median_cumulative_array_R025<- summary_cumulative_array_R025[[1]]
upper_cumulative_array_R025<- summary_cumulative_array_R025[[2]]
lower_cumulative_array_R025<- summary_cumulative_array_R025[[3]]

```
Figure 1: 
Cumulative total incident symptomatic cases across all ages: 


```{r,message=FALSE, echo=TRUE, warning=FALSE}
#figure 1:  Median daily incident cases by transmission scenarios. 


#randomly select 15 sims to show for each R_0 scenario
make_fig_1<- function(complete_data_1,complete_data_2,complete_data_3,
                      median_data_1,median_data_2,median_data_3,
                      combined_data_1,combined_data_2,combined_data_3){
random_sample_R017<- which(complete_data_1$run_index%in%sample(rep(1:500),15,replace=F))
random_sample_R021<- which(complete_data_2$run_index%in%sample(rep(1:500), 15, replace=F))
random_sample_R025<- which(complete_data_3$run_index%in%sample(rep(1:500), 15, replace = F))


incident_symptomatic_wide<- as.data.frame(cbind(median_data_1[,1],
                            apply(median_data_1[,-1],1,sum),
                            apply(median_data_2[,-1],1,sum),
                            apply(median_data_3[,-1],1,sum)))

colnames(incident_symptomatic_wide)<- c("Day", "R_0=1.7,Median", "R_0=2.1,Median", "R_0=2.5,Median") 

random_sims<- as.data.frame(cbind(combined_data_1[random_sample_R017,1],
                                apply(combined_data_1[random_sample_R017,-1],1,sum),
                                apply(combined_data_2[random_sample_R021,-1],1,sum),
                                apply(combined_data_3[random_sample_R021,-1],1,sum)))

colnames(random_sims)<- c("Day","R_0=1.7,Random", "R_0=2.1,Random", "R_0=2.5,Random")


incident_symptomatic_long<- incident_symptomatic_wide%>%
  gather(scenario, incident_symptomatic, "R_0=1.7,Median":"R_0=2.5,Median", factor_key = TRUE)

random_sims_long<- random_sims%>%
  gather(scenario, incident_symptomatic, "R_0=1.7,Random":"R_0=2.5,Random", factor_key=TRUE)


symptomatic_df<- as.data.frame(rbind(incident_symptomatic_long,random_sims_long))

symptomatic_df_sep<- symptomatic_df%>%
  separate(scenario, into=c("scenario", "summary_stat"), sep=",")%>%
  mutate(scenario=ifelse(scenario=="R_0=1.7", "Low Transmission",
                         ifelse(scenario=="R_0=2.1", "Moderate Transmission", 
                                "High Transmission")))%>%
  mutate(Day=rep(seq(as.Date('2020/03/1'),by='day',length.out=365),48))



plt_incident_cases<- ggplot(symptomatic_df_sep)+ 
  geom_line(aes(y= incident_symptomatic, x=Day,color=scenario,linetype=summary_stat))+
  #geom_ribbon(aes(ymax=upper,ymin=lower,x=Day,fill=scenario), alpha=.5) +
  labs(title="Incident Symptomatic Cases Per Day",y="Median Number of Cases") +
  labs(color="Scenario",linetype="Summary Statistic") 
return(list(plt_incident_cases,random_sample_R017,random_sample_R021,random_sample_R025))
}
f_1<- make_fig_1(complete_R017,complete_R021,complete_R025,
           median_incident_symptomatic_R017,median_incident_symptomatic_R021,
           median_incident_symptomatic_R025,
           combined_incident_R017,combined_incident_R021,combined_incident_R025)
f_1[[1]]
```

Figure 2: 

```{r, message=FALSE, warning=FALSE, echo=TRUE}
make_fig_2<- function(random_sample_1,random_sample_2,random_sample_3,
                      counts_data_1,counts_data_2,counts_data_3,
                      median_counts_data_1,median_counts_data_2,median_counts_data_3){


incident_hosp_wide<- as.data.frame(cbind(median_counts_data_1[,1,1],
                            apply(median_counts_data_1[,-1,1],1,sum),
                            apply(median_counts_data_2[,-1,1],1,sum),
                            apply(median_counts_data_3[,-1,1],1,sum)))

colnames(incident_hosp_wide)<- c("Day", "R_0=1.7,Median", "R_0=2.1,Median", "R_0=2.5,Median") 

random_sims<- as.data.frame(cbind(counts_data_1[random_sample_1,1,1],
                                apply(counts_data_1[random_sample_1,-1,1],1,sum),
                                apply(counts_data_2[random_sample_2,-1,1],1,sum),
                                apply(counts_data_3[random_sample_3,-1,1],1,sum)))

colnames(random_sims)<- c("Day","R_0=1.7,Random", "R_0=2.1,Random", "R_0=2.5,Random")


incident_hosp_long<- incident_hosp_wide%>%
  gather(scenario, incident_hosp, "R_0=1.7,Median":"R_0=2.5,Median", factor_key = TRUE)

random_sims_long<- random_sims%>%
  gather(scenario, incident_hosp, "R_0=1.7,Random":"R_0=2.5,Random", factor_key=TRUE)


hosp_df<- as.data.frame(rbind(incident_hosp_long,random_sims_long))

hosp_df_sep<- hosp_df%>%
  separate(scenario, into=c("scenario", "summary_stat"), sep=",")%>%
  mutate(scenario=ifelse(scenario=="R_0=1.7", "Low Transmission",
                         ifelse(scenario=="R_0=2.1", "Moderate Transmission", 
                                "High Transmission")))%>%
  mutate(Day=rep(seq(as.Date('2020/03/1'),by='day',length.out=365),48))



plt_hosp_cases<- ggplot(hosp_df_sep)+ 
  geom_line(aes(y= incident_hosp, x=Day,color=scenario,linetype=summary_stat))+
  #geom_ribbon(aes(ymax=upper,ymin=lower,x=Day,fill=scenario), alpha=.5) +
  labs(title="Incident Hospitalizations Per Day",y="Median Number of Hospitalizations") +
  labs(color="Scenario",linetype="Summary Statistic") 
return(plt_hosp_cases)
}
f_2<- make_fig_2(f_1[[2]],f_1[[3]],f_1[[4]],
                 counts_array_R017,counts_array_R021,counts_array_R025,
                 median_counts_array_R017,median_counts_array_R021,median_counts_array_R025)
f_2

```


Figure 3:
```{r, message=FALSE, warning=FALSE, echo=FALSE}
make_fig_3<- function(random_sample_1,random_sample_2,random_sample_3,
                      counts_data_1,counts_data_2,counts_data_3,
                      median_counts_data_1,median_counts_data_2,median_counts_data_3){


incident_death_wide<- as.data.frame(cbind(median_counts_data_1[,1,5],
                            apply(median_counts_data_1[,-1,5],1,sum),
                            apply(median_counts_data_2[,-1,5],1,sum),
                            apply(median_counts_data_3[,-1,5],1,sum)))

colnames(incident_death_wide)<- c("Day", "R_0=1.7,Median", "R_0=2.1,Median", "R_0=2.5,Median") 

random_sims<- as.data.frame(cbind(counts_data_1[random_sample_1,1,5],
                                apply(counts_data_1[random_sample_1,-1,5],1,sum),
                                apply(counts_data_2[random_sample_2,-1,5],1,sum),
                                apply(counts_data_3[random_sample_3,-1,5],1,sum)))

colnames(random_sims)<- c("Day","R_0=1.7,Random", "R_0=2.1,Random", "R_0=2.5,Random")


incident_death_long<- incident_death_wide%>%
  gather(scenario, incident_death, "R_0=1.7,Median":"R_0=2.5,Median", factor_key = TRUE)

random_sims_long<- random_sims%>%
  gather(scenario, incident_death, "R_0=1.7,Random":"R_0=2.5,Random", factor_key=TRUE)


death_df<- as.data.frame(rbind(incident_death_long,random_sims_long))

death_df_sep<- death_df%>%
  separate(scenario, into=c("scenario", "summary_stat"), sep=",")%>%
  mutate(scenario=ifelse(scenario=="R_0=1.7", "Low Transmission",
                         ifelse(scenario=="R_0=2.1", "Moderate Transmission", 
                                "High Transmission")))%>%
  mutate(Day=rep(seq(as.Date('2020/03/1'),by='day',length.out=365),48))



plt_death_cases<- ggplot(death_df_sep)+ 
  geom_line(aes(y= incident_death, x=Day,color=scenario,linetype=summary_stat))+
  #geom_ribbon(aes(ymax=upper,ymin=lower,x=Day,fill=scenario), alpha=.5) +
  labs(title="Incident Deaths Per Day",y="Median Number of Deaths") +
  labs(color="Scenario",linetype="Summary Statistic") 
return(plt_death_cases)
}
f_3<- make_fig_3(f_1[[2]],f_1[[3]],f_1[[4]],
                 counts_array_R017,counts_array_R021,counts_array_R025,
                 median_counts_array_R017,median_counts_array_R021,median_counts_array_R025)
f_3
```



Figure 4 :

```{r, message=FALSE, warning=FALSE, echo=TRUE}
make_fig_4<- function(random_sample_1,random_sample_2,random_sample_3,
                      cumulative_median_1,cumulative_median_2,cumulative_median_3,
                      cumulative_data_1,cumulative_data_2,cumulative_data_3){
 
cumulative_hosp_wide<- as.data.frame(cbind(cumulative_median_1[,1,2],
                            apply(cumulative_median_1[,-1,2],1,sum),
                            apply(cumulative_median_2[,-1,2],1,sum),
                            apply(cumulative_median_3[,-1,2],1,sum)))

colnames(cumulative_hosp_wide)<- c("Day", "R_0=1.7,Median", "R_0=2.1,Median", "R_0=2.5,Median") 

random_sims<- as.data.frame(cbind(cumulative_data_1[random_sample_1,1,2],
                                apply(cumulative_data_1[random_sample_1,-1,2],1,sum),
                                apply(cumulative_data_2[random_sample_2,-1,2],1,sum),
                                apply(cumulative_data_3[random_sample_3,-1,2],1,sum)))

colnames(random_sims)<- c("Day","R_0=1.7,Random", "R_0=2.1,Random", "R_0=2.5,Random")


cumulative_hosp_long<- cumulative_hosp_wide%>%
  gather(scenario, cumulative_hosp, "R_0=1.7,Median":"R_0=2.5,Median", factor_key = TRUE)

random_sims_long<- random_sims%>%
  gather(scenario, cumulative_hosp, "R_0=1.7,Random":"R_0=2.5,Random", factor_key=TRUE)


cumulative_hosp_df<- as.data.frame(rbind(cumulative_hosp_long,random_sims_long))

cumulative_hosp_df_sep<- cumulative_hosp_df%>%
  separate(scenario, into=c("scenario", "summary_stat"), sep=",")%>%
  mutate(scenario=ifelse(scenario=="R_0=1.7", "Low Transmission",
                         ifelse(scenario=="R_0=2.1", "Moderate Transmission", 
                                "High Transmission")))%>%
  mutate(Day=rep(seq(as.Date('2020/03/1'),by='day',length.out=365),48))



plt_cumulative_hosp<- ggplot(cumulative_hosp_df_sep)+ 
  geom_line(aes(y= cumulative_hosp, x=Day,color=scenario,linetype=summary_stat))+
  #geom_ribbon(aes(ymax=upper,ymin=lower,x=Day,fill=scenario), alpha=.5) +
  labs(title="Daily Hospital Bed Use",y="Number of Hospital Beds in Use") +
  labs(color="Scenario",linetype="Summary Statistic") 



###########################
 
cumulative_ICU_wide<- as.data.frame(cbind(cumulative_median_1[,1,3],
                            apply(cumulative_median_1[,-1,3],1,sum),
                            apply(cumulative_median_2[,-1,3],1,sum),
                            apply(cumulative_median_3[,-1,3],1,sum)))

colnames(cumulative_ICU_wide)<- c("Day", "R_0=1.7,Median", "R_0=2.1,Median", "R_0=2.5,Median") 

random_sims<- as.data.frame(cbind(cumulative_data_1[random_sample_1,1,3],
                                apply(cumulative_data_1[random_sample_1,-1,3],1,sum),
                                apply(cumulative_data_2[random_sample_2,-1,3],1,sum),
                                apply(cumulative_data_3[random_sample_3,-1,3],1,sum)))

colnames(random_sims)<- c("Day","R_0=1.7,Random", "R_0=2.1,Random", "R_0=2.5,Random")


cumulative_ICU_long<- cumulative_ICU_wide%>%
  gather(scenario, cumulative_ICU, "R_0=1.7,Median":"R_0=2.5,Median", factor_key = TRUE)

random_sims_long<- random_sims%>%
  gather(scenario, cumulative_ICU, "R_0=1.7,Random":"R_0=2.5,Random", factor_key=TRUE)


cumulative_ICU_df<- as.data.frame(rbind(cumulative_ICU_long,random_sims_long))

cumulative_ICU_df_sep<- cumulative_ICU_df%>%
  separate(scenario, into=c("scenario", "summary_stat"), sep=",")%>%
  mutate(scenario=ifelse(scenario=="R_0=1.7", "Low Transmission",
                         ifelse(scenario=="R_0=2.1", "Moderate Transmission", 
                                "High Transmission")))%>%
  mutate(Day=rep(seq(as.Date('2020/03/1'),by='day',length.out=365),48))



plt_cumulative_ICU<- ggplot(cumulative_ICU_df_sep)+ 
  geom_line(aes(y= cumulative_ICU, x=Day,color=scenario,linetype=summary_stat))+
  #geom_ribbon(aes(ymax=upper,ymin=lower,x=Day,fill=scenario), alpha=.5) +
  labs(title="Daily ICU Bed Use",y="Number of ICU Beds in Use") +
  labs(color="Scenario",linetype="Summary Statistic") 

############################
 
cumulative_vent_wide<- as.data.frame(cbind(cumulative_median_1[,1,4],
                            apply(cumulative_median_1[,-1,4],1,sum),
                            apply(cumulative_median_2[,-1,4],1,sum),
                            apply(cumulative_median_3[,-1,4],1,sum)))

colnames(cumulative_vent_wide)<- c("Day", "R_0=1.7,Median", "R_0=2.1,Median", "R_0=2.5,Median") 

random_sims<- as.data.frame(cbind(cumulative_data_1[random_sample_1,1,4],
                                apply(cumulative_data_1[random_sample_1,-1,4],1,sum),
                                apply(cumulative_data_2[random_sample_2,-1,4],1,sum),
                                apply(cumulative_data_3[random_sample_3,-1,4],1,sum)))

colnames(random_sims)<- c("Day","R_0=1.7,Random", "R_0=2.1,Random", "R_0=2.5,Random")


cumulative_vent_long<- cumulative_vent_wide%>%
  gather(scenario, cumulative_vent, "R_0=1.7,Median":"R_0=2.5,Median", factor_key = TRUE)

random_sims_long<- random_sims%>%
  gather(scenario, cumulative_vent, "R_0=1.7,Random":"R_0=2.5,Random", factor_key=TRUE)


cumulative_vent_df<- as.data.frame(rbind(cumulative_vent_long,random_sims_long))

cumulative_vent_df_sep<- cumulative_vent_df%>%
  separate(scenario, into=c("scenario", "summary_stat"), sep=",")%>%
  mutate(scenario=ifelse(scenario=="R_0=1.7", "Low Transmission",
                         ifelse(scenario=="R_0=2.1", "Moderate Transmission", 
                                "High Transmission")))%>%
  mutate(Day=rep(seq(as.Date('2020/03/1'),by='day',length.out=365),48))



plt_cumulative_vent<- ggplot(cumulative_vent_df_sep)+ 
  geom_line(aes(y= cumulative_vent, x=Day,color=scenario,linetype=summary_stat))+
  #geom_ribbon(aes(ymax=upper,ymin=lower,x=Day,fill=scenario), alpha=.5) +
  labs(title="Daily Vent Use",y="Number of Vents in Use") +
  labs(color="Scenario",linetype="Summary Statistic") 

return(list(plt_cumulative_hosp,plt_cumulative_ICU,plt_cumulative_vent))
}

f_4<- make_fig_4(f_1[[2]],f_1[[3]],f_1[[4]],
           median_cumulative_array_R017,median_cumulative_array_R021,median_cumulative_array_R025,
           cumulative_array_R017,cumulative_array_R021,cumulative_array_R025)
f_4[[1]]   
f_4[[2]]
f_4[[3]]
```

New(but actually old) figure 5:
```{r, message=FALSE, warning=FALSE, echo=TRUE}
#cumulative cases (symptomatic)
#cumulative sum of incident cases for each of the 500 sims
make_fig_5<- function(combined_data_1,combined_data_2,combined_data_3,
                      cumulative_data_1,cumulative_data_2,cumulative_data_3){
daily_incident_cases<- matrix(NA,nrow(combined_data_1),ncol=4)

daily_incident_cases[,1]<- combined_data_1[,1]
daily_incident_cases[,2]<- apply(combined_data_1[,-1],1,sum)
daily_incident_cases[,3]<- apply(combined_data_2[,-1],1,sum)
daily_incident_cases[,4]<- apply(combined_data_3[,-1],1,sum)

cumulative_cases_symptomatic<- matrix(NA, nrow(daily_incident_cases), ncol(daily_incident_cases))
cumulative_cases_symptomatic[,1]<- combined_data_1[,1]
cumulative_cases_symptomatic[which(cumulative_cases_symptomatic[,1]==1),]<- 
  daily_incident_cases[which(daily_incident_cases[,1]==1),]
for(i in 2:365){
  for(j in 2: ncol(daily_incident_cases)){
    cumulative_cases_symptomatic[which(cumulative_cases_symptomatic[,1]==i),j]<-
      cumulative_cases_symptomatic[which(cumulative_cases_symptomatic[,1]==(i-1)),j]+
      daily_incident_cases[which(daily_incident_cases[,1]==i),j]
  }
  
}

median_cumulative_cases_symptomatic<- matrix(NA, 365, ncol= 4)

median_cumulative_cases_symptomatic[,1]<- rep(1:365)
for(i in 1:nrow(median_cumulative_cases_symptomatic)){
  median_cumulative_cases_symptomatic[i,-1]<- 
    apply(cumulative_cases_symptomatic[which(cumulative_cases_symptomatic[,1]==i),-1],2,median)
}

cumulative_cases_symptomatic<- as.data.frame(median_cumulative_cases_symptomatic)
colnames(cumulative_cases_symptomatic)<- c("Day", "Low Transmission",
                                          "Moderate Transmission", "High Transmission")

cumulative_cases_symptomatic_long<- cumulative_cases_symptomatic%>%
  gather(scenario, cumulative_cases, "Low Transmission": "High Transmission", factor_key = T)%>%
  mutate(Day= rep(seq(as.Date('2020/03/1'),by="day", length.out = 365),3))



cumulative_symptomatic_cases_plt<- ggplot(cumulative_cases_symptomatic_long)+
  geom_line(aes(x=Day, y= cumulative_cases, color=scenario))+
  labs(y="Median Cumulative Symptomatic Cases", title= "Median Cumulative Symptomatic Cases",
       color="Scenario")

#cumulative deaths
cumulative_deaths<- as.data.frame(cbind(rep(1:nrow(cumulative_data_1[,,5])),
                    apply(cumulative_data_1[,-1,5],1,sum),
                    apply(cumulative_data_2[,-1,5],1,sum),
                    apply(cumulative_data_3[,-1,5],1,sum)))


median_cumulative_deaths<- matrix(NA, 365, 4)
median_cumulative_deaths[,1]<- rep(1:365)
for(i in 1:nrow(median_cumulative_deaths)){

    median_cumulative_deaths[i,-1]<- 
      apply(cumulative_deaths[which(cumulative_deaths[,1]==i),-1],2,median)
  
}

colnames(median_cumulative_deaths)<- c("Day", "Low Transmission", "Moderate Transmission", 
                                       "High Transmission")

median_cumulative_deaths<- as.data.frame(median_cumulative_deaths)

median_cumulative_deaths_long<- median_cumulative_deaths%>%
  gather(scenario, cumulative_death, "Low Transmission": "High Transmission", factor_key = T)%>%
   mutate(Day= rep(seq(as.Date('2020/03/1'),by="day", length.out = 365),3))


cumulative_deaths_plot<- ggplot(median_cumulative_deaths_long)+
  geom_line(aes(x=Day, y= cumulative_death, color=scenario))+
  labs(y= "Median Deaths", title="Median Deaths",color="Scenario")

return(list(cumulative_symptomatic_cases_plt,cumulative_deaths_plot))
}
f_5<- make_fig_5(combined_incident_R017,combined_incident_R021,combined_incident_R025,
                 cumulative_array_R017,cumulative_array_R021,cumulative_array_R025)

f_5[[1]]
f_5[[2]]
```





Table 1:
```{r, message=FALSE, echo=TRUE, warning=FALSE}

wide_incident_cases<- t(as.data.frame(cbind(incident_cases_R017_75,incident_cases_R021_75,
                                            incident_cases_R025_75)))
                      
wide_incident_lowbound<- t(as.data.frame(cbind(incident_cases_lower_R017_75,
                      incident_cases_lower_R021_75,incident_cases_lower_R025_75)))
                      
wide_incident_upbound<- t(as.data.frame(cbind(incident_cases_upper_R017_75,
                      incident_cases_upper_R021_75,incident_cases_upper_R025_75)))
                                      
                                      



wide_hosp_cases<- t(as.data.frame(cbind(apply(cumulative_array_median_R017_75[,,2],1,sum),
                    apply(cumulative_array_median_R021_75[,,2],1,sum),
                    apply(cumulative_array_median_R025_75[,,2],1,sum))))
                      
wide_hosp_lowbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_lower_R017_75[,,2],1,sum),
                      apply(cumulative_array_IQR_lower_R021_75[,,2],1,sum),
                      apply(cumulative_array_IQR_lower_R025_75[,,2],1,sum))))
                      
wide_hosp_upbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_upper_R017_75[,,2],1,sum),
                      apply(cumulative_array_IQR_upper_R021_75[,,2],1,sum),
                      apply(cumulative_array_IQR_upper_R025_75[,,2],1,sum))))



wide_ICU_cases<- t(as.data.frame(cbind(apply(cumulative_array_median_R017_75[,,3],1,sum),
                    apply(cumulative_array_median_R021_75[,,3],1,sum),
                    apply(cumulative_array_median_R025_75[,,3],1,sum))))
                      
wide_ICU_lowbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_lower_R017_75[,,3],1,sum),
                      apply(cumulative_array_IQR_lower_R021_75[,,3],1,sum),
                      apply(cumulative_array_IQR_lower_R025_75[,,3],1,sum))))
                      
wide_ICU_upbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_upper_R017_75[,,3],1,sum),
                      apply(cumulative_array_IQR_upper_R021_75[,,3],1,sum),
                      apply(cumulative_array_IQR_upper_R025_75[,,3],1,sum))))




wide_vent_cases<- t(as.data.frame(cbind(apply(cumulative_array_median_R017_75[,,4],1,sum),
                    apply(cumulative_array_median_R021_75[,,4],1,sum),
                    apply(cumulative_array_median_R025_75[,,4],1,sum))))
                      
wide_vent_lowbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_lower_R017_75[,,4],1,sum),
                      apply(cumulative_array_IQR_lower_R021_75[,,4],1,sum),
                      apply(cumulative_array_IQR_lower_R025_75[,,4],1,sum))))
                      
wide_vent_upbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_upper_R017_75[,,4],1,sum),
                      apply(cumulative_array_IQR_upper_R021_75[,,4],1,sum),
                      apply(cumulative_array_IQR_upper_R025_75[,,4],1,sum))))



wide_death_cases<- t(as.data.frame(cbind(apply(cumulative_array_median_R017_75[,,5],1,sum),
                    apply(cumulative_array_median_R021_75[,,5],1,sum),
                    apply(cumulative_array_median_R025_75[,,5],1,sum))))
                      
wide_death_lowbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_lower_R017_75[,,5],1,sum),
                      apply(cumulative_array_IQR_lower_R021_75[,,5],1,sum),
                      apply(cumulative_array_IQR_lower_R025_75[,,5],1,sum))))
                      
wide_death_upbound<- t(as.data.frame(cbind(apply(cumulative_array_IQR_upper_R017_75[,,5],1,sum),
                      apply(cumulative_array_IQR_upper_R021_75[,,5],1,sum),
                      apply(cumulative_array_IQR_upper_R025_75[,,5],1,sum))))

max_date_may<- which(wide_hosp_cases[3,]==max(wide_hosp_cases[3,61:91]))
max_date_june<- which(wide_hosp_cases[3,]==max(wide_hosp_cases[3,92:121]))
max_date_july<- which(wide_hosp_cases[3,]==max(wide_hosp_cases[3,122:152]))
max_date_august<- which(wide_hosp_cases[3,]==max(wide_hosp_cases[3,153:183]))



cumulative_time_groups <- rbind(cbind(wide_incident_cases[,max_date_may],
                        wide_incident_lowbound[,max_date_may],wide_incident_upbound[,max_date_may],
                        wide_incident_cases[,max_date_june],wide_incident_lowbound[,max_date_june],
                        wide_incident_upbound[,max_date_june],wide_incident_cases[,max_date_july],
                        wide_incident_lowbound[,max_date_july],wide_incident_upbound[,max_date_july],
                        wide_incident_cases[,max_date_august],wide_incident_lowbound[,max_date_august],
                        wide_incident_upbound[,max_date_august]),
                        cbind(wide_hosp_cases[,max_date_may],wide_hosp_lowbound[,max_date_may],
                        wide_hosp_upbound[,max_date_may],wide_hosp_cases[,max_date_june],
                        wide_hosp_lowbound[,max_date_june],wide_hosp_upbound[,max_date_june],
                        wide_hosp_cases[,max_date_july],wide_hosp_lowbound[,max_date_july],
                        wide_hosp_upbound[,max_date_july],wide_hosp_cases[,max_date_august],
                        wide_hosp_lowbound[,max_date_august],wide_hosp_upbound[,max_date_august]),
                        cbind(wide_ICU_cases[,max_date_may],wide_ICU_lowbound[,max_date_may],
                        wide_ICU_upbound[,max_date_may],wide_ICU_cases[,max_date_june],
                        wide_ICU_lowbound[,max_date_june],wide_ICU_upbound[,max_date_june],
                        wide_ICU_cases[,max_date_july],wide_ICU_lowbound[,max_date_july],
                        wide_ICU_upbound[,max_date_july],wide_ICU_cases[,max_date_august],
                        wide_ICU_lowbound[,max_date_august],wide_ICU_upbound[,max_date_august]),
                        cbind(wide_vent_cases[,max_date_may],wide_vent_lowbound[,max_date_may],
                        wide_vent_upbound[,max_date_may],wide_vent_cases[,max_date_june],
                        wide_vent_lowbound[,max_date_june],wide_vent_upbound[,max_date_june],
                        wide_vent_cases[,max_date_july],wide_vent_lowbound[,max_date_july],
                        wide_vent_upbound[,max_date_july],wide_vent_cases[,max_date_august],
                        wide_vent_lowbound[,max_date_august],wide_vent_upbound[,max_date_august]),
                        cbind(wide_death_cases[,max_date_may],wide_death_lowbound[,max_date_may],
                        wide_death_upbound[,max_date_may],wide_death_cases[,max_date_june],
                        wide_death_lowbound[,max_date_june],wide_death_upbound[,max_date_june],
                        wide_death_cases[,max_date_july],wide_death_lowbound[,max_date_july],
                        wide_death_upbound[,max_date_july],wide_death_cases[,max_date_august],
                        wide_death_lowbound[,max_date_august],wide_death_upbound[,max_date_august]))


dim(cumulative_time_groups)

colnames(cumulative_time_groups)<- c("Median","25th","75th",
                                     "Median ","25th ", "75th ", 
                                     "Median  ","25th  ", "75th  ",
                                     "Median   ", "25th   ", "75th   ")

rownames(cumulative_time_groups)<- c("R_0=1.7","R_0=2.1","R_0=2.5","R_0=1.7 ",
                                     "R_0=2.1 ","R_0=2.5 ",
                                     "R_0=1.7  ",
                                     "R_0=2.1  ","R_0=2.5  ",
                                     "R_0=1.7   ","R_0=2.1   ","R_0=2.5   ",
                                     "R_0=1.7     ","R_0=2.1     ","R_0=2.5     ")
mode(cumulative_time_groups)<-"integer"

cumulative_time_groups<- as.data.frame(cumulative_time_groups)

kable(cumulative_time_groups)%>%
  kable_styling()%>%
  pack_rows("Symptomatic Infections",1,3)%>%
  pack_rows("Hospitalizations",4,6)%>%
  pack_rows("ICU Beds",7,9)%>%
  pack_rows("Vents",10,12)%>%
  pack_rows("Death",13,15)%>%
  add_header_above(c(" "=1, "May, 2020"=3, "June, 2020"=3, "July, 2020"=3, "August, 2020"=3))

```


Table 2: 

```{r, message=FALSE, warning=FALSE, echo=TRUE}


wide_incident_cases<- t(as.data.frame(cbind(data_combined_cats_median_R017_75,
                                            data_combined_cats_median_R021_75,
                                            data_combined_cats_median_R025_75)))
                      
wide_incident_lowbound<- t(as.data.frame(cbind(data_combined_cats_IQR_lower_R017_75,
                                               data_combined_cats_IQR_lower_R021_75,
                                               data_combined_cats_IQR_lower_R021_75)))

wide_incident_upbound<- t(as.data.frame(cbind(data_combined_cats_IQR_upper_R017_75,
                                               data_combined_cats_IQR_upper_R021_75,
                                               data_combined_cats_IQR_upper_R021_75)))                               
                                      



wide_hosp_cases<- t(as.data.frame(cbind(cumulative_array_median_R017_75[,,2],
                    cumulative_array_median_R021_75[,,2],
                    cumulative_array_median_R025_75[,,2])))
                      
wide_hosp_lowbound<- t(as.data.frame(cbind(cumulative_array_IQR_lower_R017_75[,,2],
                      cumulative_array_IQR_lower_R021_75[,,2],
                      cumulative_array_IQR_lower_R025_75[,,2])))
                      
wide_hosp_upbound<- t(as.data.frame(cbind(cumulative_array_IQR_upper_R017_75[,,2],
                      cumulative_array_IQR_upper_R021_75[,,2],
                      cumulative_array_IQR_upper_R025_75[,,2])))



wide_ICU_cases<- t(as.data.frame(cbind(cumulative_array_median_R017_75[,,3],
                    cumulative_array_median_R021_75[,,3],
                    cumulative_array_median_R025_75[,,3])))
                      
wide_ICU_lowbound<- t(as.data.frame(cbind(cumulative_array_IQR_lower_R017_75[,,3],
                      cumulative_array_IQR_lower_R021_75[,,3],
                      cumulative_array_IQR_lower_R025_75[,,3])))
                      
wide_ICU_upbound<- t(as.data.frame(cbind(cumulative_array_IQR_upper_R017_75[,,3],
                      cumulative_array_IQR_upper_R021_75[,,3],
                      cumulative_array_IQR_upper_R025_75[,,3])))




wide_vent_cases<- t(as.data.frame(cbind(cumulative_array_median_R017_75[,,4],
                    cumulative_array_median_R021_75[,,4],
                    cumulative_array_median_R025_75[,,4])))
                      
wide_vent_lowbound<- t(as.data.frame(cbind(cumulative_array_IQR_lower_R017_75[,,4],
                      cumulative_array_IQR_lower_R021_75[,,4],
                      cumulative_array_IQR_lower_R025_75[,,4])))
                      
wide_vent_upbound<- t(as.data.frame(cbind(cumulative_array_IQR_upper_R017_75[,,4],
                      cumulative_array_IQR_upper_R021_75[,,4],
                      cumulative_array_IQR_upper_R025_75[,,4])))



wide_death_cases<- t(as.data.frame(cbind(cumulative_array_median_R017_75[,,5],
                    cumulative_array_median_R021_75[,,5],
                    cumulative_array_median_R025_75[,,5])))
                      
wide_death_lowbound<- t(as.data.frame(cbind(cumulative_array_IQR_lower_R017_75[,,5],
                      cumulative_array_IQR_lower_R021_75[,,5],
                      cumulative_array_IQR_lower_R025_75[,,5])))
                      
wide_death_upbound<- t(as.data.frame(cbind(cumulative_array_IQR_upper_R017_75[,,5],
                      cumulative_array_IQR_upper_R021_75[,,5],
                      cumulative_array_IQR_upper_R025_75[,,5])))



cumulative_time_groups <- rbind(cbind(wide_incident_cases[,max_date_may],
                        wide_incident_lowbound[,max_date_may],wide_incident_upbound[,max_date_may],
                        wide_incident_cases[,max_date_june],wide_incident_lowbound[,max_date_june],
                        wide_incident_upbound[,max_date_june],wide_incident_cases[,max_date_july],
                        wide_incident_lowbound[,max_date_july],wide_incident_upbound[,max_date_july],
                        wide_incident_cases[,max_date_august],wide_incident_lowbound[,max_date_august],
                        wide_incident_upbound[,max_date_august]),
                        cbind(wide_hosp_cases[,max_date_may],wide_hosp_lowbound[,max_date_may],
                        wide_hosp_upbound[,max_date_may],wide_hosp_cases[,max_date_june],
                        wide_hosp_lowbound[,max_date_june],wide_hosp_upbound[,max_date_june],
                        wide_hosp_cases[,max_date_july],wide_hosp_lowbound[,max_date_july],
                        wide_hosp_upbound[,max_date_july],wide_hosp_cases[,max_date_august],
                        wide_hosp_lowbound[,max_date_august],wide_hosp_upbound[,max_date_august]),
                        cbind(wide_ICU_cases[,max_date_may],wide_ICU_lowbound[,max_date_may],
                        wide_ICU_upbound[,max_date_may],wide_ICU_cases[,max_date_june],
                        wide_ICU_lowbound[,max_date_june],wide_ICU_upbound[,max_date_june],
                        wide_ICU_cases[,max_date_july],wide_ICU_lowbound[,max_date_july],
                        wide_ICU_upbound[,max_date_july],wide_ICU_cases[,max_date_august],
                        wide_ICU_lowbound[,max_date_august],wide_ICU_upbound[,max_date_august]),
                        cbind(wide_vent_cases[,max_date_may],wide_vent_lowbound[,max_date_may],
                        wide_vent_upbound[,max_date_may],wide_vent_cases[,max_date_june],
                        wide_vent_lowbound[,max_date_june],wide_vent_upbound[,max_date_june],
                        wide_vent_cases[,max_date_july],wide_vent_lowbound[,max_date_july],
                        wide_vent_upbound[,max_date_july],wide_vent_cases[,max_date_august],
                        wide_vent_lowbound[,max_date_august],wide_vent_upbound[,max_date_august]),
                        cbind(wide_death_cases[,max_date_may],wide_death_lowbound[,max_date_may],
                        wide_death_upbound[,max_date_may],wide_death_cases[,max_date_june],
                        wide_death_lowbound[,max_date_june],wide_death_upbound[,max_date_june],
                        wide_death_cases[,max_date_july],wide_death_lowbound[,max_date_july],
                        wide_death_upbound[,max_date_july],wide_death_cases[,max_date_august],
                        wide_death_lowbound[,max_date_august],wide_death_upbound[,max_date_august]))


dim(cumulative_time_groups)

colnames(cumulative_time_groups)<- c("Median","25th","75th",
                                     "Median ","25th ", "75th ", 
                                     "Median  ","25th  ", "75th  ",
                                     "Median   ", "25th   ", "75th   ")

rownames(cumulative_time_groups)<-c("Age 0-19","Age 20-34","Age 35-59","Age60-74",
                                    "Age 75+","HCW","Homeless",
                                    "Age 0-19 ","Age 20-34 ","Age 35-59 ","Age60-74 ",
                                    "Age 75+ ","HCW ","Homeless ",
                                    "Age 0-19  ","Age 20-34  ","Age 35-59  ","Age60-74  ",
                                    "Age 75+  ","HCW  ","Homeless  ",
                                    "Age 0-19   ","Age 20-34   ","Age 35-59   ","Age60-74   ",
                                    "Age 75+   ","HCW   ","Homeless   ",
                                    "Age 0-19    ","Age 20-34    ","Age 35-59    ","Age60-74    ",
                                    "Age 75+    ","HCW    ","Homeless    ",
                                    "Age 0-19     ","Age 20-34     ","Age 35-59     ","Age60-74     ",
                                    "Age 75+     ","HCW     ","Homeless     ",
                                    "Age 0-19      ","Age 20-34      ","Age 35-59      ","Age60-74      ",
                                    "Age 75+      ","HCW      ","Homeless      ",
                                    "Age 0-19       ","Age 20-34       ","Age 35-59       ","Age60-74       ",
                                    "Age 75+       ","HCW       ","Homeless       ",
                                    "Age 0-19        ","Age 20-34        ","Age 35-59        ","Age60-74        ",
                                    "Age 75+        ","HCW        ","Homeless        ",
                                    "Age 0-19         ","Age 20-34         ","Age 35-59         ","Age60-74         ",
                                    "Age 75+         ","HCW         ","Homeless         ",
                                    "Age 0-19          ","Age 20-34          ","Age 35-59          ","Age60-74          ",
                                    "Age 75+          ","HCW          ","Homeless          ",
                                    "Age 0-19           ","Age 20-34           ","Age 35-59           ","Age60-74           ",
                                    "Age 75+           ","HCW           ","Homeless           ",
                                    "Age 0-19            ","Age 20-34            ","Age 35-59            ","Age60-74            ",
                                    "Age 75+            ","HCW            ","Homeless            ",
                                    "Age 0-19             ","Age 20-34             ","Age 35-59             ","Age60-74             ",
                                    "Age 75+             ","HCW             ","Homeless             ",
                                    "Age 0-19              ","Age 20-34              ","Age 35-59              ","Age60-74              ",
                                    "Age 75+              ","HCW              ","Homeless               ")
mode(cumulative_time_groups)<-"integer"

cumulative_time_groups<- as.data.frame(cumulative_time_groups)

kable(cumulative_time_groups)%>%
  kable_styling()%>%
  pack_rows("Symptomatic Infections, R_0=1.7",1,7)%>%
  pack_rows("Symptomatic Infections, R_0=2.1",8,14)%>%
  pack_rows("Symptomatic Infections, R_0=2.5",15,21)%>%
  pack_rows("Hospitalizations, R_0=1.7",22,28)%>%
  pack_rows("Hospitalizations, R_0=2.1",29,35)%>%
  pack_rows("Hospitalizations, R_0=2.5",36,42)%>%
  pack_rows("ICU Beds, R_0=1.7",43,49)%>%
  pack_rows("ICU Beds, R_0=2.1",50,56)%>%
  pack_rows("ICU Beds, R_0=2.5",57,63)%>%
  pack_rows("Vents, R_0=1.7",64,70)%>%
  pack_rows("Vents, R_0=2.1",71,77)%>%
  pack_rows("Vents, R_0=2.5",78,84)%>%
  pack_rows("Death, R_0=1.7",85,91)%>%
  pack_rows("Death, R_0=2.1",92,98)%>%
   pack_rows("Death, R_0=2.5",99,105)%>%
  add_header_above(c(" "=1, "May, 2020"=3, "June, 2020"=3, "July, 2020"=3, "August, 2020"=3))



```
